Reproducible research course project 1(submit on 150118)
========================================================

##1, Loading and preprocessing the data
First, we load the data(activity.csv) into act.
Next, we remove the row which contain NA.
```{r}
#1-1,load the file
setwd("C:/Users/namazu/Desktop/150112_reproducibleResearch/repdata-data-activity")

act<-read.csv("activity.csv")

#1-2 preprocessing the data by removing data which contain NA.
act_noNA<-act
act_noNA<-act[complete.cases(act),]
levelList_noNA<-levels(act_noNA$date)

```

##2, What is mean total number of steps taken per day?
#2-1. Make a histogram of the total number of steps taken each day
```{r}
steps_eachday_noNA_sum<-vector()
for (j in 1:length(levelList_noNA)){
  part<-subset(act_noNA,act_noNA$date==levelList_noNA[j])
  partSteps<-part$steps
  partSteps_df<-as.data.frame(partSteps)
  steps_eachday_noNA_sum[j]<-apply(partSteps_df,2,sum)
}


barplot(steps_eachday_noNA_sum,names.arg=levelList_noNA,xlab="date",ylab="sum of steps in each day",main="sum of steps in each day")
```

#2-2. Calculate and report the mean and median total number of steps taken per day
```{r}

steps_eachday_noNA_mean<-vector()
steps_eachday_noNA_median<-vector()
for (j in 1:length(levelList_noNA)){
  part<-subset(act_noNA,act_noNA$date==levelList_noNA[j])
  partSteps<-part$steps
  partSteps_df<-as.data.frame(partSteps)
  steps_eachday_noNA_mean[j]<-apply(partSteps_df,2,mean)
  steps_eachday_noNA_median[j]<-apply(partSteps_df,2,median)
}


#integrate the results into one dataframe
mean_median_df<-cbind(steps_eachday_noNA_mean,steps_eachday_noNA_median)
colnames(mean_median_df)<-c("mean of steps in each day","median of steps in each day")

mean_median_df
```


##3 What is the average daily activity pattern?
#3-1. Make a time series plot (i.e. type = "l" ) of the 5minute interval (xaxis) and the average number of steps taken, averaged across all days (yaxis)

```{r}
#make interval data
intervals<-vector()
for ( k in 0:471){
  intervals[k+1]<-5*k
}

#calculate mean of steps in each interval value.
steps_eachInterval_mean<-vector()
for ( k in 0:471){
  partInt<-subset(act_noNA,act_noNA$interval==k*5)
  partIntSteps<-as.data.frame(partInt$steps)
  partIntSteps<-as.data.frame(partIntSteps[complete.cases(partIntSteps),])
  partIntSteps
  steps_eachInterval_mean[k+1]<-apply(partIntSteps,2,mean)
}

#making the dataframe to report the mean of steps in each interval
steps_eachInterval_mean<-cbind(intervals,steps_eachInterval_mean)
colnames(steps_eachInterval_mean)<-c("intervals","mean of steps in each interval")
steps_eachInterval_mean

#make time series plot
plot(steps_eachInterval_mean[,2] ~ steps_eachInterval_mean[,1],type="l",xlab="5minute interval",ylab="averaged steps in each interval",main="time seriese plot of \n averaged steps in each interval") 

```

#3-2  Which 5minute interval, on average across all the days in the dataset, contains the maximum number of steps?

my answer: According to the calculation below, when the interval is 835, the mean of the steps in each interval is maximized.

```{r}
#get the value of max of the mean of the steps in each interval
maxSteps<-max(steps_eachInterval_mean[,2],na.rm=TRUE)
#get the value of intervals which has maxSteps
maxdata<-subset(steps_eachInterval_mean,steps_eachInterval_mean[,2]==maxSteps)
maxdata 

```


##4 Imputing missing values
#4-1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NA)

my answer :
According to the calculation below, the number of NAs in this dataset was 2304.
```{r}
NAnum<-sum(is.na(act))
NAnum 

```

#4-2. Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5minute interval, etc.

my answer:
We fill NAs in this dataset with mean steps in each interval.

#4-3.Create a new dataset that is equal to the original dataset but with the missing data filled in.





